\documentclass[a4paper,article,14pt]{extarticle}
\usepackage{spbudiploma_tempora}
\usepackage{euscript, longtable, makecell, textcomp}
\usepackage[pdftex]{graphicx}
\usepackage{amsthm, amssymb, amsmath}

\begin{document}

\input{titlepage_ru.tex}
\input{titlepage_en.tex}

\tableofcontents
\pagebreak

\input{introduction.tex}
\input{work_purpose.tex}
\input{literature_review.tex}
\input{chapter_1.tex}
\input{chapter_2.tex}
\input{conclusions.tex}

\begin{thebibliography}{1}

\bibitem{bizone2023} Компания BI.ZONE (2023). \flqq Число мошеннических сайтов в 2023 году выросло на 86\%\frqq. URL: \url{https://bi.zone/news/chislo-moshennicheskikh-saytov-v-2023-godu-vyroslo-na-86/}.

\bibitem{cbr2024} Центральный банк России (2024). \flqq Обзор операций, совершенных без согласия клиентов финансовых организаций\frqq. URL: \url{https://www.cbr.ru/analytics/ib/operations_survey/2023/}.

\bibitem{cheng2023} Cheng D., Ye Y., Xiang S., Ma Z., Zhang Y., Jiang, C. (2023). \flqq Anti-Money Laundering by Group-Aware Deep Graph Learning\frqq. IEEE Transactions on Knowledge and Data Engineering.

\bibitem{ding2023} Ding Z., Shi J., Li Q., Cao J. (2023). \flqq Effective Multi-Graph Neural Networks for Illicit Account Detection on Cryptocurrency Transaction Networks\frqq. arXiv preprint, 2309.02460.

\bibitem{dou2020} Dou, Y., Liu, Z., Sun, L., Deng, Y., Peng, H., Yu, P. S. (2020). \flqq Enhancing Graph Neural Network-based Fraud Detectors against Camouflaged Fraudsters\frqq. Proceedings of the 29th ACM international conference on information \& knowledge management, 315--324.

\bibitem{hamilton2017} Hamilton W., Ying Z., Leskovec J. (2017). \flqq Inductive Representation Learning on Large Graphs\frqq. Advances in neural information processing systems, 30.

\bibitem{hu2023} Hu S., Zhang Z., Luo B., Lu S., He B., Liu L. (2023). \flqq BERT4ETH: A Pre-trained Transformer for Ethereum Fraud Detection\frqq. Proceedings of the ACM Web Conference 2023, 2189--2197.

\bibitem{jesus2022} Jesus S., Pombal J., Alves D., Cruz A., Saleiro P., Ribeiro R. P., Gama J., Bizarro P. (2022). \flqq Turning the Tables: Biased, Imbalanced, Dynamic Tabular Datasets for ML Evaluation\frqq. Advances in Neural Information Processing Systems, 35, 33563--33575.

\bibitem{kim2023} Kim H., Choi J., Whang J. J. (2023) \flqq Dynamic Relation-Attentive Graph Neural Networks for Fraud Detection\frqq. 2023 IEEE International Conference on Data Mining Workshops (ICDMW), 1092--1096.

\bibitem{kipf2017} Kipf T. N., Welling M. (2017). \flqq Semi-Supervised Classification with Graph Convolutional Networks\frqq. International Conference on Learning Representations.

\bibitem{li2023} Li S., Qiao B., Li K., Lu Q., Lin M., Zhou W. (2023). \flqq Multi-modal Social Bot Detection: Learning Homophilic and Heterophilic Connections Adaptively\frqq. Proceedings of the 31st ACM International Conference on Multimedia, 3908--3916.

\bibitem{pan2023} Pan J., Wong S. L., Yuan Y. (2023). \flqq RAGLog: Log Anomaly Detection using Retrieval Augmented Generation\frqq. arXiv preprint, 2311.05261.

\bibitem{pozzolo2015} Pozzolo D. A., Caelen O., Johnson R. A., Bontempi G. (2015). \flqq Calibrating Probability with Undersampling for Unbalanced Classification\frqq. 2015 IEEE symposium series on computational intelligence, 159--166.

\bibitem{qin2022} Qin, Z., Liu, Y., He, Q., Ao, X. (2022). \flqq Explainable Graph-based Fraud Detection via Neural Meta-graph Search\frqq. ACM '22 International Conference on Information \& Knowledge Management, 4414--4418.

\bibitem{rampavsek2022} Rampášek L., Galkin M., Dwivedi V. P., Luu A. T., Wolf G., Beaini D. (2022). \flqq Recipe for a General, Powerful, Scalable Graph Transformer\frqq. Advances in Neural Information Processing Systems, 35, 14501--14515.

\bibitem{shirzad2023} Shirzad H., Velingker A., Venkatachalam B., Sutherland D. J., Sinop A. K. (2023). \flqq Exphormer: Sparse Transformers for Graphs\frqq. International Conference on Machine Learning, 31613--31632.

\bibitem{sotiropoulos2023} Sotiropoulos K., Zhao L., Liang P. J.,  Akoglu L. (2023). \flqq ADAMM: Anomaly Detection of Attributed Multi-graphs with Metadata: A Unified Neural Network Approach\frqq. 2023 IEEE International Conference on Big Data (BigData), 865--874.

\bibitem{tian2023} Tian, S., Dong, J., Li, J., Zhao, W., Xu, X., Song, B., Meng, C., Zhang, T. and Chen, L (2023). \flqq SAD: Semi-Supervised Anomaly Detection on Dynamic Graphs\frqq. arXiv preprint, 2305.13573.

\bibitem{vaswani2017} Vaswani A., Shazeer N., Parmar N., Uszkoreit J., Jones L., Gomez A. N., Kaiser L., Polosukhin I. (2017). \flqq Attention Is All You Need\frqq. Advances in neural information processing systems, 30.

\bibitem{velickovic2017} Veličković P., Cucurull G., Casanova A., Romero A., Liò P., Bengio Y. (2017). \flqq Graph Attention Networks\frqq. International Conference on Learning Representations, 1050, 20, 10--48550.

\bibitem{wang2023} Wang Y., Zhang J., Huang Z., Li W., Feng S., Ma Z., Sun Y., Yu D., Dong F., Jin J., Wang B., Luo J. (2023). \flqq Label Information Enhanced Fraud Detection against Low Homophily in Graphs\frqq. Proceedings of the ACM Web Conference 2023, 406--416.

\bibitem{xiang2023} Xiang S., Zhu M., Cheng D., Li E., Zhao R., Ouyang Y., Chen L., Zheng Y. (2023). \flqq Semi-supervised Credit Card Fraud Detection via Attribute-Driven Graph Representation\frqq. Proceedings of the AAAI Conference on Artificial Intelligence, 37, 12, 14557--14565.

\bibitem{yin2024} Yin S., Zhu P., Wu L., Gao C., Wang Z. (2024). \flqq GAMC: An Unsupervised Method for Fake News Detection Using Graph Autoencoder with Masking\frqq. Proceedings of the AAAI Conference on Artificial Intelligence, 38, 1, 347--355.

\end{thebibliography}
\end{document}
